A quantitative analysis of Media Agenda and Public Opinion using time-evolving topic distribution

### 2018-09-11 bmc_article.tex
Cambios en el formato de Author Contribution

\section*{Author's contributions}
P.B. conceived the study. S.P. collected and analysed most of the data. F.A. collected Twitter data; F.A., P.B, and S.P. interpreted the data and prepared the manuscript. P.B. and C.O.D  give the final approval of the version to be published.

>>>>

\section*{Author's contributions}
PB conceived the study. SP collected and analysed most of the data. FA collected Twitter data. FA, PB, and SP interpreted the data and prepared the manuscript. PB and COD  give the final approval of the version to be published.
